---
title: "Shane Viola"
---

## About Me

I am a graduate student at Baruch College pursuing an M.S. in Business Analytics. I currently work in financial planning and analysis at NYCHA, where I focus on budgeting, forecasting, financial modeling, and process improvement.

My background combines finance, analytics, and technology. I am especially interested in using data, automation, and analytical tools to improve decision-making and streamline financial processes.

## Experience

I currently work as an Economist/Supervisor at NYCHA, where I support financial planning and analysis for the Section 8 program. My work includes forecasting, budget analysis, revenue and expense modeling, and developing tools that improve reporting and planning processes.

## Education

**Baruch College**  
M.S. in Artificial Intelligence and Business Analytics | Expected 2028

## Baruch College

I am currently pursuing my M.S. in Artificial Intelligence and Business Analytics at Baruch College.

```{r}
#| echo: false
#| message: false
#| warning: false

if(!require("leaflet")){
    options(repos=c(CRAN="https://cloud.r-project.org"))
    install.packages("leaflet")
    stopifnot(require("leaflet"))
}

baruch_longitude <- -73.98333
baruch_latitude  <- +40.74028

leaflet() |>
  addTiles() |>
  setView(baruch_longitude, baruch_latitude, zoom=17) |>
  addPopups(baruch_longitude, baruch_latitude, 
            "I am a Master's student at <b>Baruch College</b>!")
```

**SUNY Old Westbury**  
B.S. in Finance | 2022  
GPA: 4.00/4.00

## Skills

- Advanced Excel
- SQL
- R
- Python
- Power BI
- Power Query
- VBA
- Financial Modeling
- Forecasting
- Data Analysis
- Process Automation



```{r}
#| include: false
1+1
```

--------------

Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`